---
title: "Analysis Report"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(lme4)
library(ggplot2)
library(performance)
library(DHARMa)
library(see)
```

# 1. Overview

This report documents the statistical analyses, model comparisons, and diagnostic checks for the thesis data.

# 2. Data Preparation

```{r}
head(final_data)
```

# 3. Hypothesis 1 – Hedonic Condition: √n and Judgment Strength

## 3.1 Model Summaries

```{r}
summary(model_linear_h1)
summary(model_mixed_h1)
summary(model_mixed_rs_h1)
anova(model_mixed_h1, model_mixed_rs_h1)
summary(model_covariate)
```

## 3.2 Correlation & Plot

```{r}
cor.test(data_hedonic$rating, sqrt(data_hedonic$n))
plot_h1
```

# 4. Hypothesis 2 – Interaction: √n × Condition

```{r}
summary(model_linear_h2)
summary(model_mixed_h2)
summary(model_mixed_rs_h2)
anova(model_mixed_h2, model_mixed_rs_h2)
summary(model_covariate_h2)
```

```{r}
ggplot(final_data, aes(x = sqrt(n), y = rating, color = cond)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Interaction: Condition × √n", x = "√ Sample Size", y = "Judgment Strength") +
  theme_minimal()
```

# 5. Hypothesis 3 – Judgment Confidence

```{r}
summary(model_linear_h3)
summary(model_mixed_h3)
summary(model_mixed_rs_h3)
summary(model_covariate_h3)
```

```{r}
ggplot(final_data, aes(x = sqrt(n), y = confidence, color = cond)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Confidence: √n × Condition", x = "√ Sample Size", y = "Confidence") +
  theme_minimal()
```

# 6. Hypothesis 4 – Diagnosticity and Sampling

```{r}
summary(model_mixed_diag)
summary(model_cond)
```

```{r}
ggplot(final_data, aes(x = candidatePositivity, y = sqrt(n), color = cond)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Diagnosticity × Condition", x = "Candidate Positivity", y = "√ Sample Size") +
  theme_minimal()
```

# 7. Model Fit Summary Tables

```{r}
fit_stats_h1
fit_stats_h2
fit_stats_h3
fit_stats_h4
```

# 8. Session Info

```{r}
sessionInfo()
```
